Parsing Postfix log files

### 2007-03-26 doc/logparser.tex
Added an example rule and documentation for the new restriction_name field in rules.

@@

>>>>

    \item [restriction\_name] The restriction which caused the mail to be
        rejected.  Only applicable to rules which have a result of
        \texttt{rejected}, other rules will have an empty string.

@@

\subsection{Example rule}

This example rule matches the message Postfix logs when it rejects mail
from a sender address where the domain has neither an MX record nor an A
record, i.e. mail could not be delivered to the sender's address.  
For full details see
http://www.postfix.org/postconf.5.html\#reject\_unknown\_sender\_domain

% Don't reformat this!
\begin{tabular}[]{ll}

name                & Unknown sender domain                             \\
description         & We do not accept mail from unknown domains        \\
program             & postfix/smtpd                                     \\
restriction\_name   & reject\_unknown\_sender\_domain                   \\
regex               & \verb!^<(__SENDER__)>: Sender address rejected: ! \\
                    & \verb!  Domain not found; from=<\1> !             \\
                    & \verb!  to=<(__RECIPIENT__)> proto=E?SMTP !       \\
                    & \verb!  helo=<(__HELO__)>$!                       \\
result\_cols        & recipient = 2; sender = 1                         \\
connection\_cols    & helo = 3                                          \\
result\_data        &                                                   \\
connection\_data    &                                                   \\
result              & REJECTED                                          \\
action              & SAVE\_BY\_PID                                     \\
queueid             & 0                                                 \\
rule\_order         & 0                                                 \\
priority            & 0                                                 \\

\end{tabular}
